HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
more shortening

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units,
or {\it atomic}. In most cases, atomic units
correspond to individual words, but they may also correspond to unanalyzable
multi-word expressions, i.e., expressions that do not have meaningful sub-units
(e.g., idioms like ``takes two to tango'').
When a multi-word unit is labeled as atomic, its sub-units' annotations are discarded
from the evaluation.

>>>>

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units,
or {\it atomic}. In most cases, atomic units
correspond to individual words, but they may also correspond to unanalyzable
multi-word expressions.
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.
